\documentclass[11pt,letterpaper]{article}
%\documentstyle[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{xfrac}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[version = 3]{mhchem}
\usepackage{chemstyle}
\usepackage{graphicx}
\usepackage{epstopdf}
%\usepackage{tabularx,ragged2e,booktabs,caption}
%\newcolumntype{C}[1]{>{\Centering}m{#1}}
%\renewcommand\tabularxcolumn[1]{C{#1}}
%\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{subcaption} 
\usepackage{caption}
\usepackage[left=1cm,right=1cm,top=0.5cm,bottom=2cm]{geometry}
%\usepackage{siunitx}



\begin{document}
\setlength{\parindent}{0cm} 



\frenchspacing

% Default margins are too wide all the way around. I reset them here
%\setlength{\topmargin}{-.5in}
%\setlength{\textheight}{9in}
%\setlength{\oddsidemargin}{.125in}
%\setlength{\evensidemargin}{.125in}
\setlength{\textwidth}{6.25in}

\title {\Large{\textbf{Student Self Reflection}}\\ \large{CENG 340--Introduction to Environmental Engineering\\
Instructor: Deborah Sills\\ \textbf{In Class: September 20, 2013}}}

\author {}
\date {}
\maketitle

\vspace{-1.5cm}
\textbf{Name:}\\

We are four weeks into the semester.  Some of you are doing great, but a number of you are confused by the material and struggling.  Next week on Monday I will ask for anonymous course evaluations of my teaching that will hopefully help me adapt (where I can) and change things I'm doing (if possible) that are not helping you learn.  I will take all of your feedback seriously.  I want all of you to succeed in this class, and I'm pretty sure you all can.\\

On the flip side, you are also responsible for your learning, and today I'm asking you to reflect and think about what you have been doing in this class---good and bad. (Note: This is a self reflection.  On Monday, you will have the opportunity to evaluate me and the course.)

\section *{How are things going?}
Items you \emph{might} discuss: Why do you think your struggling with this course? How much time do you spend on problem sets?  When do you start problems sets?  Do you work with friends?  Do you read the text? Do you read the text when you don't know how to solve a problem?  When you're confused, do you contact me to ask questions?

\vspace{2.4in}

\section *{How you might improve your learning strategies and do better?}








\end{document}