Lab 1--Total Dissolved Solids analysis
========================================================
Before starting an R session, you must call up the R-packages needed for your analysis.

```{r warning=FALSE, message = FALSE}
library(plyr)
library(ggplot2)
```

Total dissolved solids measurements are reported below.

```{r}
Frac <- c(149660,148620,148060, 148231)
Treated <- c(77820,76160,77840,77830)
```

Create a data fram with the two sample types to make it easier to conduct analysis and make plots""
```{r}
Frac_samp <- data.frame(SampleType = c(rep("Frac", 4), 
             rep("Treated", 4)),
             TDS = c(Frac, Treated))
```
OK, now the fun part, we want to determine if the treated water contains significantly less TDS than the untreated water. We will adress this question in two ways: (1) plot the mean values of each sample type and include error bars that represent 95% confidence intervals; (2) conduct a two-sample t-test anda Wilcoxon Signed Rank Test to determine if the data sets are significantly different.

To plot the mean values ± 95% CIs, we must first calculate the mean and standard error.

```{r}
se <- function(x) sd(x)/sqrt(length(x))
Frac_new <- ddply(Frac_samp, .(SampleType), summarize, mean = mean(TDS),
CI = qt(0.975, 3)*se(TDS))
```
Plot the means as bar graphs with error bars that represnet 95% confidence intervals:
```{r fig.width=5.5, fig.height=4.5}
ggplot(Frac_new, aes(x = SampleType, y = mean, ymin = mean - CI, ymax = mean + CI)) +
  geom_bar(stat="identity", color = "light blue", fill = "light blue") + 
  geom_errorbar(width=0.15) + 
  labs(x = "Treatment", y = "\nMean TDS (mg/L)") 
```


Now do a t-test

```{r}
t.test(TDS ~ SampleType, data = Frac_samp,  var.equal = FALSE)
```

